Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-07 volunteer-clouds-ieee-ci-si.tex
Adding graphs

It is interesting also to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows a S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds. The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, and of the order of
10 seconds. As it can be seen, it drops sharply implying there are
just a few of them, and with diminishing probability as time
decreases.

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{img/puts-openshift-4-4.png}
\includegraphics[width=0.32\linewidth]{img/puts-openshift-4-24.png}
\includegraphics[width=0.32\linewidth]{img/puts-openshift-7-31.png}
\caption{Number of {\tt PUT}s per unique IP and fit to a Generalized
  Extreme Value distribution (in red). From left to right, experiments 4/4, 4/24 and 7/31.}
\label{fig:puts:os}
\end{figure}
%

It is interesting also to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows a S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds. The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, and of the order of
10 seconds. As it can be seen, it drops sharply implying there are
just a few of them, and with diminishing probability as time
decreases. This exponential distribution also appears in the
distribution of HTTP {\tt PUT}s, equivalent to the number of
generations divided by 100, contributed by every user, which is shown
in Figure \ref{fig:put:os}.
